Association between trauma severity models and opportunities for improvement:

### 2024-06-09 manuscript.Rmd
committing old changes

---
title: 'Association between trauma severity models and opportunities for improvement:
  A retrospective cohort study'
author: "Victoria Witthoff"
output:
  bookdown::word_document2: default
  bookdown::html_document2: default
  bookdown::pdf_document2: default
bibliography: bibliography.bib
csl: vancouver.csl
fontsize: 11pts
linestretch: 1
always_allow_html: yes
editor_options: 
   chunk_output_type: inline
---

>>>>

---
title: 'Association between trauma severity models and opportunities for improvement:
  A retrospective cohort study'
author: "Victoria Witthoff"
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2: default
bibliography: bibliography.bib
csl: vancouver.csl
fontsize: 11pts
linestretch: 1
always_allow_html: yes
editor_options: 
   chunk_output_type: inline
---
